|

### 2023-08-25 JCGS_response_to_reviews/response_to_review.Rmd

*Comments to the Author*

*I did not need any convincing that residual diagnostic plots are superior to tests but this paper presents a narrower argument to support this claim than many analysts would employ. For example, diagnostic plots may reveal features which are not directly connected to a linear model assumption and yet are interesting and important to identify. Of course, it is difficult to justify a journal article on the basis of such observations. In this respect, I am impressed that you have succeeded in demonstrating the superiority within the more formal framework of the lineup protocol. You have restricted attention to the residual-fitted plot and a particular selection of formal tests. I accept that this was necessary to make definite progress. Nevertheless, it would be good to add some discussion of the wider picture.*

Thank for this feedback. We are happy to see that, like many people, you don't need convincing and that you are glad to see that we have succeeded in demonstrating the superiority of residual diagnostic plots.

We have added more explanation of the use of residual plots in the Introduction and we have added a section Limitations and practicality where the broader picture is discussed.

@@

*1. "The ubiquity of this advice is curious: investigating why, is the subject of this paper. " I don't find this advice curious - it seems almost universal. I have taught this topic for many years and give the same advice. I explain why I give this advice and I believe several other authors do the same. Their reasons are wider in scope than you express in this article.*

We have changed the language to focus on that is the advice is given despite the lack of empirical evidence.

@@

*This article uses the lineup protocol in a visual inference experiment, which puts a residual plot in the context of null plots. Focus is mostly on detecting nonlinearities and heteroskedasticity. Comparisons with some classic tests are given.*

*Overall Comments*

*Overall, this paper is very well written and interesting. However, I have some serious reservations about the practicality of the procedure, which I articulate in greater detail below. I also think the paper is currently too long, and that a significant chunk of material should be shifted to the Appendix.*

Thanks for the positive feedback. We have shortened the paper by XXX pages. We have expanded the explanations of why the practicality of the procedure should not be questioned in Section XXX.

@@

*1. As mentioned above, the paper is too long. While the onus should be on the authors for getting the page number down, some possible suggestions could be combining Sections 1 and 2 while moving some of the historical context (which I fully acknowledge is quite interesting) to the Appendix, and moving some of the technical details of Section 3.2 to the Appendix.*

See the response above, thanks for your suggestions. We have moved most of Section 3.2 Statistical significance to the Appendix. (how we shorten the rest of the paper XXX)

- Part of Experimental design -> appendix
- Part of Explanations of the lineup (p-value) -> appendix
- Shorten the Section 1 and 2 (more precise)
- Modify the discussion and conclusion to address the issues raised by reviews

@@

*2. The practical implementation of this as a procedure is, in my opinion, the biggest weakness. The authors acknowledge the costliness of human evaluation of residuals, but not until Page 33, Line 47. I find this a tad disingenuous as this will likely jump out to the reader as being a problem right from the beginning of reading this paper (it did for me). So I think being upfront about this limitation, and providing some practical considerations to address this concern will assuage my concerns. There might be some concepts from human-computer interaction that could be effective for operationalizing and improving the efficiency of the present work.*

The new Section Limitations and practicality addresses these concerns and we have added a sentence in Introduction so that the reader will not be concerned upfront.

@@

*3. I think a better connection needs to be made with where this computationally expensive process could potentially pay off. For example, applying the lineup protocol to, say, any of the data examples in the texts cited by the authors would amount to nothing more than an academic exercise. But, what sort of data problems can the authors point to and definitively claim that the lineup protocol will be invaluable at ensuring we visually capture possible nonlinearities or heteroskedasticity? I am not doubting the efficacy of the approach, but I’d like to see a stronger case made with its practical application.*

As mentioned above,

This is not computationally expensive. The conventional test also make mistakes. You need something more than the conventional test. And you also need something more than the residual plot.

check earlier paper.

@@

*4. What should be claimed about the sample size n as a limitation? Take in point the comments at the bottom of page 19. Am I to understand that the lineup protocol will not be appropriate for big data problems?*

This is a display issue not a lineup protocol issue.

*5. At the beginning of Section 4.2.3, what cultural biases do the authors anticipate by restricting the participants to be “fluent in English”? Granted this is likely done as a matter of convenience, but it would be good to articulate how cultural biases may be present in interpreting a lineup protocol.*

The instruction of this study was in English.
very unlikely there will be a difference between English speaker and non-English speaker.

@@

*6. I would like the authors to be a little clearer about their specific contributions. I felt as if the biggest contribution in this work was the experiments that they did. A lot of references are included for work that is applied in this manuscript, so at times I got lost as to what already existed in the literature and what “new” material the authors were giving the reader.*

We have clarified the language of the Introduction and the Conclusion.

### 2023-08-25 paper.Rmd
update responses

In addition, scatterplots of residuals plotted against the fitted values and each of the explanatory variables, can be used to scrutinize their relationships. If there are any visually discoverable patterns, the model is potentially inadequate or incorrectly specified. **Interesting features that are not directly connected to a linear model assumption can also be found from residual plots, such as the discreteness of the fitted values, outliers and influential points.** In general, one looks for noticeable departures from the model such as non-linear pattern or heteroskedasticity. A non-linear pattern would suggest that the model needs to have some additional non-linear terms. Heteroskedasticity suggests that the error is dependent on the predictors, and hence violates the independence assumption. However, correctly judging whether NO pattern exists in a residual plot is a difficult task for humans. Humans will almost always see a pattern (see @kahneman2011thinking), so the question that really needs answering is whether any pattern perceived is consistent with randomness, purely sampling variability, or noise. It is especially difficult to teach this to new analysts and students [@loy2021bringing]. To address this, statistical tests are available to check for non-linear patterns [e.g. @ramsey1969tests], and heteroskedasticity  [e.g. @breusch1979simple].

**There are other types of residual plot to extract the available information and identify inappropriate assumptions, like the added variable plot for studying the role of an external variable if it enters linearly into a model. Partial residual plots have been suggested as cornputationally convenient substitutes for the added variable plots. For use in diagnostic procedures, several transformations of the ordinary residuals have been suggested to overcome partially some of their shortcomings. Studentized residuals have null distributions that are independent of the scale parameters. These residuals are shown to be closely related to a mean shift model for outliers and to the residuals obtained when each case in turn is left out of the data. Alternatively. the residuals can be transformed to have a selected covariance structure: The usual suggestion is to obtain residuals with uncorrelated elements.**

Linear regression is a well-established procedure, and there is considerable literature describing diagnostic procedures, e.g. @draper1998applied, @montgomery1982introduction, @belsley1980regression, @cook1999applied and @cook1982residuals. Interestingly, despite the abundance of conventional tests, ALL of these writings advise that plotting residuals is an essential tool for diagnosing regression model problems:

@@

\noindent The common wisdom of experts is that plotting the residuals is indispensable for diagnosing model fits. The ubiquity of this advice is *curious*: investigating why, is the subject of this paper.

@@

>>>>

In addition, scatterplots of residuals plotted against the fitted values and each of the explanatory variables, can be used to scrutinize their relationships. If there are any visually discoverable patterns, the model is potentially inadequate or incorrectly specified. **Interesting features that are not directly connected to a linear model assumption can also be found from residual plots, such as the discreteness of the fitted values, outliers and influential points.** In general, one looks for noticeable departures from the model such as non-linear pattern or heteroskedasticity. A non-linear pattern would suggest that the model needs to have some additional non-linear terms. Heteroskedasticity suggests that the error is dependent on the predictors, and hence violates the independence assumption.

However, correctly judging whether NO pattern exists in a residual plot is a difficult task for humans. Humans will almost always see a pattern (see @kahneman2011thinking), so the question that really needs answering is whether any pattern perceived is consistent with randomness, purely sampling variability, or noise. It is especially difficult to teach this to new analysts and students [@loy2021bringing]. To address this, statistical tests are available to check for non-linear patterns [e.g. @ramsey1969tests], and heteroskedasticity  [e.g. @breusch1979simple].

**There are other types of residual plot to extract the available information and identify inappropriate assumptions, like the added variable plot (cite here) for studying the role of an external variable if it enters linearly into a model. Partial residual plots (cite here) have been suggested as computationally convenient substitutes for the added variable plots. For use in diagnostic procedures, several transformations of the ordinary residuals have been suggested to overcome partially some of their shortcomings. Studentized residuals (cite here) have null distributions that are independent of the scale parameters. These residuals are shown to be closely related to a mean shift model for outliers and to the residuals obtained when each case in turn is left out of the data. Alternatively. the residuals can be transformed to have a selected covariance structure: The usual suggestion is to obtain residuals with uncorrelated elements.**

There is sustainable literature describing diagnostic procedures for linear models, e.g. @draper1998applied, @montgomery1982introduction, @belsley1980regression, @cook1999applied and @cook1982residuals. Interestingly, despite the abundance of conventional tests, ALL of these writings advise that plotting residuals is an essential tool for diagnosing regression model problems:

@@

\noindent The common wisdom of experts is that plotting the residuals is indispensable for diagnosing model fits. The lack of empirical evidence for the ubiquitous advice is *curious*. The research study discussed in this paper fills this gap.

@@

# Limitations and practicality

- explain how the lineup protocol can be cheaply done with the R package "nullabor". everyone can do it easily. The cost of using lineup in stat education under classroom setting is cheap (adam loy teaching paper)
- Formal tests. reliable results. crowd sourcing is not expensive compared to the cost other devices in the lab and is not entirely unreasonable. Only if there is grey area (you can not confidently detect the data).
- The possiblity of computer vision in the future.

- repeat the scope of the study
- list other things we could have tested
- explain why the result should apply to other residual diagnostics settings 
- finding interesting feature that was not intended to test for
